Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-12 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
finished corrections on supp

Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield.

@@

\includegraphics[scale=0.27]{plots/RC_factor.png}

@@

Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.

@@

\includegraphics[scale=0.27]{plots/BC_factor.png}

@@

statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{bc,1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{bc,2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,2}}$)

@@

\includegraphics[scale=0.3]{plots/Em_syst.png}

@@

\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated using the Barlow ratio approach described above.
In this case, the ratio was calculated from the difference between the experimental cross sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections.

@@

\includegraphics[scale=0.3]{plots/rad_sys.png}

@@

\includegraphics[scale=0.3]{plots/bc_sys.png}
\caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering corrections.}

@@

Figures \ref{fig:rad_sys} and \ref{fig:bc_sys} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that

>>>>

Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data yield. The uncertainty in the radiative
correction factor was determined by the Monte-Carlo statistics from the simulation. The large uncertainty in the lowest momentum bin, $p_{\mathrm{r}} = 0.02\pm0.02$, can
be understood from the fact that statistics were limited in this phase space region as indicated by the "hole" observed at $p_{\mathrm{r}} = 0.02$ in Fig. \ref{fig:Pm_Ps} (right). 

@@

\includegraphics[scale=0.26]{plots/RC_factor.png}

@@

Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section. The
uncertainty in the bin-centering correction factor was determined from the standard error propagation of a ratio between two quantities. 

@@

\includegraphics[scale=0.26]{plots/BC_factor.png}

@@

statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)

@@

\includegraphics[scale=0.4]{plots/Em_syst.png}

@@

\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated
using the Barlow ratio approach described above. In this case, the ratio was calculated from the difference between the experimental cross
sections using the Laget PWIA and FSI models for both radiative and bin-centering corrections. Figures \ref{fig:rad_sys} and \ref{fig:bc_sys}
show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that

@@

\includegraphics[scale=0.31]{plots/rad_sys.png}

@@

\includegraphics[scale=0.31]{plots/bc_sys.png}
\caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering correction systematics.}

@@
